Template for Grading Scientific Computing Software

### 2020-04-21 StateOfPractice/Peter-Notes/GradingTemplate.tex

  \midrule
  \textbf{Installability} (Measured via installation on a virtual machine.)\\
  \midrule
 \pmi{Are required (known to work) operating system versions listed?}\\
  Are there installation instructions? (\{yes, no\})\\
  Are the installation instructions linear? (\{yes, no, n/a\})\\
  Is there something in place to automate the installation? (\{yes$^*$, no\})\\
Is there a specified way to validate the installation, such as a test suite?
(\{yes$^*$, no\})\\
How many steps were involved in the installation? (number) \\
How many software packages need to be installed before or during
installation?(number) \\
\pmi{are specific versions of required packages listed?}\\
\pmi{are there links to or instructions for the installation of required packages?}\\
Run uninstall, if available. Were any obvious problems caused? (\{unavail,
yes$^*$, no\})\\
\pmi{In your opinion could a non-developer of the software effectively install this software by verbatim following the instructions}\\
\pmi{Was troubleshooting the instructions necessary to install the system?}
  Overall impression? (\{1 .. 10\})\\

@@

  Are external libraries used? (\{yes$^*$, no, unclear\})\\
  \pmi{are versions of external libraries specified?}\\
  \pmi{are instructions for finding/installing the external libraries specified?}\\
  Does the community have confidence in this library? (\{yes, no, unclear\})\\
  Any reference to the requirements specifications of the program?
(\{yes$^*$, no, unclear\})\\
What tools or techniques are used to build confidence of correctness?
(string)\\
If there is a getting started tutorial, is the output as expected? (\{yes,
no$^*$, n/a\})\\
\pmi{Does the getting started tutorial provide an answer to verify against?}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Did the software ``break'' during installation? (\{yes$^*$, no\})\\
  \pmi{was a helpful error message provided?}
    \pmi{was the installation recoverable?}
Did the software ``break'' during the initial tutorial testing? (\{yes$^*$, no,
n/a\})\\
  \pmi{was a helpful error message provided?}\\
  \pmi{was the testing recoverable?}\\
  Overall impression? (\{1 .. 10\})\\

@@

Does the software handle garbage input reasonably? (\{yes, no$^*$\}) \\
  For any plain text input files, if all new lines are replaced with new lines
  and carriage returns, will the software handle this gracefully? (\{yes,
  no$^*$, n/a\})\\
  \pmi{Does the system react gracefully when required libraries or input files are not provided? Descriptive message?}
  Overall impression? (\{1 .. 10\})\\

@@

  Is there evidence that performance was considered? (\{yes$^*$, no\})\\
  \pmi{Does the software (optionally) use GPU for processing?}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Is there a getting started tutorial? (\{yes, no\})\\
  Is there a standard example that is explained? (\{yes, no\})\\
  \pmi{Is a solution provided?}\\
  Is there a user manual? (\{yes, no\})\\
  Does the application have the usual ``look and feel'' for the platform it is
  on? (\{yes, no$^*$\})\\
  \pmi{this question is vague to me}\\
  Are there any features that show a lack of visibility? (\{yes, no$^*$\})\\
  Are expected user characteristics documented? (\{yes, no\})\\
What is the user support model? (string)\\
  Overall impression? (\{1 .. 10\})\\

@@

Is there a history of multiple versions of the software? (\{yes, no,
unclear\})\\
  Is there any information on how code is reviewed, or how to contribute?
  (\{yes$^*$, no\})\\
  Is there a changelog?  (\{yes, no\})\\
What is the maintenance type? (set of \{corrective, adaptive, perfective,
unclear\})\\
  What issue tracking tool is employed? (set of \{Trac, JIRA, Redmine, e-mail,
discussion board, sourceforge, google code, git, none, unclear\})\\
Are the majority of identified bugs fixed? (\{yes, no$^*$, unclear\})\\
What is the percentage of identified issues that are closed?
(percentage)\\
\pmi{is there a way to measure average time to close issues?}\\
\pmi{are files well commented? - percentage?}\\
\pmi{comment on module / file size}\\
Which version control system is in use? (\{svn, cvs, git, github, unclear\})\\
Is there evidence that maintainability was considered in the design?
  (\{yes$^*$, no\})\\
Are there code clones? (\{yes$^*$, no, unclear\})\\
  Overall impression? (\{1 .. 10\})\\

@@

Are any portions of the software used by another package? (\{yes$^*$,
no\})\\
  Is there evidence that reusability was considered in the design? (API
documented, web service, command line tools, ...) (\{yes$^*$, no, unclear\})\\
\pmi{Are module interfaces clearly defined?}\\
\pmi{Are modules described in the user guide?}\\
\pmi{Is the system modularized?}\\
Overall impression? (\{1 .. 10\})\\

@@

  What platforms is the software advertised to work on?
  (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  \pmi{What versions of these platforms is the software advertised to work on?}\\
  \pmi{How many external libraries are needed?}\\
  Are special steps taken in the source code to handle portability? (\{yes$^*$,
  no, n/a\}) \\
  Is portability explicitly identified as NOT being important? (\{yes, no\})\\
Convincing evidence that portability has been achieved? (\{yes$^*$,
no\})\\
  Overall impression? (\{1 .. 10\})\\

>>>>

  \midrule
  \textbf{Installability} (Measured via installation on a virtual machine.)\\
  \midrule
 \pmi{Are required (known to work) operating system versions listed? (\{yes, no\})}\\
  Are there installation instructions? (\{yes, no\})\\
  Are the installation instructions linear? (\{yes, no, n/a\})\\
  Is there something in place to automate the installation? (\{yes$^*$, no\})\\
Is there a specified way to validate the installation, such as a test suite?
(\{yes$^*$, no\})\\
How many steps were involved in the installation? (number) \\
How many software packages need to be installed before or during
installation?(number) \\
\pmi{are specific versions of required packages listed? (\{yes, no, n/a\})}\\
\pmi{are there links to or instructions for the installation of required packages? (\{yes, no, n/a\})}\\
Run uninstall, if available. Were any obvious problems caused? (\{unavail,
yes$^*$, no\})\\
\pmi{In your opinion could a non-developer of the software effectively install this software by verbatim following the instructions (\{yes, no, n/a\})}\\
\pmi{Was troubleshooting the instructions necessary to install the system? (\{yes, no, n/a\})}
  Overall impression? (\{1 .. 10\})\\

@@

  Are external libraries used? (\{yes$^*$, no, unclear\})\\
  \pmi{are versions of external libraries specified? (\{yes, no, n/a\})}\\
  Does the community have confidence in this library? (\{yes, no, unclear\})\\
  Any reference to the requirements specifications of the program?
(\{yes$^*$, no, unclear\})\\
What tools or techniques are used to build confidence of correctness?
(string)\\
If there is a getting started tutorial, is the output as expected? (\{yes,
no$^*$, n/a\})\\
\pmi{Does the getting started tutorial provide an answer to verify against? (\{yes, no, n/a\})}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Did the software ``break'' during installation? (\{yes$^*$, no\})\\
  \pmi{was a helpful error message provided? (\{yes, no, n/a\})}
    \pmi{was the installation recoverable? (\{yes, no, n/a\})}
Did the software ``break'' during the initial tutorial testing? (\{yes$^*$, no,
n/a\})\\
  \pmi{was a helpful error message provided? (\{yes, no, n/a\})}\\
  \pmi{was the testing recoverable? (\{yes, no, n/a\})}\\
  Overall impression? (\{1 .. 10\})\\

@@

Does the software handle garbage input reasonably? (\{yes, no$^*$\}) \\
  For any plain text input files, if all new lines are replaced with new lines
  and carriage returns, will the software handle this gracefully? (\{yes,
  no$^*$, n/a\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Is there evidence that performance was considered? (\{yes$^*$, no\})\\
  \pmi{Does the software (optionally) use GPU for processing? (\{yes, no, unclear\})}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Is there a getting started tutorial? (\{yes, no\})\\
  Is there a standard example that is explained? (\{yes, no\})\\
  \pmi{Is a solution provided? (\{yes, no, n/a\})}\\
  Is there a user manual? (\{yes, no\})\\
  Does the application have the usual ``look and feel'' for the platform it is
  on? (\{yes, no$^*$\})\\
  Are there any features that show a lack of visibility? (\{yes, no$^*$\})\\
  Are expected user characteristics documented? (\{yes, no\})\\
What is the user support model? (string)\\
  Overall impression? (\{1 .. 10\})\\

@@

Is there a history of multiple versions of the software? (\{yes, no,
unclear\})\\
  Is there any information on how code is reviewed, or how to contribute?
  (\{yes$^*$, no\})\\
  Is there a changelog?  (\{yes, no\})\\
 \pmi{Is technical documentation (requirements, architecture, code, algorithms, interfaces, APIs) provided? (\{yes, no, unclear\})}\\ 
What is the maintenance type? (set of \{corrective, adaptive, perfective,
unclear\})\\
  What issue tracking tool is employed? (set of \{Trac, JIRA, Redmine, e-mail,
discussion board, sourceforge, google code, git, none, unclear\})\\
Are the majority of identified bugs fixed? (\{yes, no$^*$, unclear\})\\
What is the percentage of identified issues that are closed?
(percentage)\\
\pmi{Are files well commented? (\{yes, no, unclear\})}\\
\pmi{Are files of reasonable length? (\{yes, no, unclear\})}\\
Which version control system is in use? (\{svn, cvs, git, github, unclear\})\\
Is there evidence that maintainability was considered in the design?
  (\{yes$^*$, no\})\\
Are there code clones? (\{yes$^*$, no, unclear\})\\
  Overall impression? (\{1 .. 10\})\\

@@

Are any portions of the software used by another package? (\{yes$^*$,
no\})\\
  Is there evidence that reusability was considered in the design? (API
documented, web service, command line tools, ...) (\{yes$^*$, no, unclear\})\\
\pmi{Is the system modularized? (\{yes, no, unclear\})}\\
\pmi{Are module interfaces clearly defined? (\{yes, no, n/a\})}\\
\pmi{Are modules described in the user guide? (\{yes, no, n/a\})}\\
Overall impression? (\{1 .. 10\})\\

@@

  What platforms is the software advertised to work on?
  (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  \pmi{Are versions of these platforms specified? (\{yes,
  	no\})}\\
  \pmi{How many external libraries are needed to be manually installed? (\{int, unclear\})}\\
  Are special steps taken in the source code to handle portability? (\{yes$^*$,
  no, n/a\}) \\
  Is portability explicitly identified as NOT being important? (\{yes, no\})\\
Convincing evidence that portability has been achieved? (\{yes$^*$,
no\})\\
  Overall impression? (\{1 .. 10\})\\
